\documentclass[a4 paper]{article}
\usepackage[inner=2.0cm,outer=2.0cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{setspace}
\usepackage[ruled]{algorithm2e}
\usepackage[rgb]{xcolor}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{amsgen,amsmath,amstext,amsbsy,amsopn,tikz,amssymb,tkz-linknodes}
\usepackage{fancyhdr}
\usepackage[colorlinks=true, urlcolor=blue,  linkcolor=blue, citecolor=blue]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{rotating}
\usepackage{booktabs}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\numberwithin{equation}{section}

\newcommand{\homework}[6]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{page}{1}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf CSE 211:~Discrete Mathematics \hfill {\small (#2)}} }
       \vspace{6mm}
       \hbox to 6.28in { {\Large \hfill #1  \hfill} }
       \vspace{6mm}
       \hbox to 6.28in { {\it Instructor: {\rm #3} \hfill Name: Abdullah Enes Patır {\rm #5} \hfill Student Id: 200104004005 {\rm #6}} \hfill}
       \hbox to 6.28in { {\it Assistant: #4  \hfill #6}}
      \vspace{2mm}}
   }
   \end{center}
   \markboth{#5 -- #1}{#5 -- #1}
   \vspace*{4mm}
}

\newcommand{\problem}[2]{~\\\fbox{\textbf{Problem #1}}\hfill (#2 points)\newline\newline}
\newcommand{\subproblem}[1]{~\newline\textbf{(#1)}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Hy}{\mathcal{H}}
\newcommand{\VS}{\textrm{VS}}
\newcommand{\solution}{~\newline\textbf{\textit{(Solution)}} }

\newcommand{\bbF}{\mathbb{F}}
\newcommand{\bbX}{\mathbb{X}}
\newcommand{\bI}{\mathbf{I}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\bepsilon}{\boldsymbol{\epsilon}}
\newcommand{\balpha}{\boldsymbol{\alpha}}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\0}{\mathbf{0}}


\begin{document}
\homework{Homework \#1}{Due: 30/10/22}{Dr. Zafeirakis Zafeirakopoulos}{Başak Karakaş}{}{}
\textbf{Course Policy}: Read all the instructions below carefully before you start working on the assignment, and before you make a submission.
\begin{itemize}
\item It is not a group homework. Do not share your answers to anyone in any circumstance. Any cheating means at least -100 for both sides. 
\item Do not take any information from Internet.
\item No late homework will be accepted. 
\item For any questions about the homework, send an email to bkarakas2018@gtu.edu.tr
\item Use LaTeX. You can work on the tex file shared with you in the assignment document.
\item Submit both the tex and pdf files into Homework1. Name of the files should be "\emph{SurnameName$\_$Id.tex}" and "\emph{SurnameName$\_$Id.pdf}".
\end{itemize}

\problem{1: Sets}{3+3+3+3+3=15}
Which of the following sets are equal? Show your work step by step.\newline
\subproblem{a} $\{$t : t is a root of $x^2$ – 6x + 8 = 0$\}$
\newline
\subproblem{b} $\{$y : y is a real number in the closed interval [2, 3]$\}$
\newline
\subproblem{c} $\{$4, 2, 5, 4$\}$
\newline
\subproblem{d} $\{$4, 5, 7, 2$\}$ - $\{$5, 7$\}$
\newline
\subproblem{e} $\{$q: q is either the number of sides of a rectangle or the number of digits in any integer between 11 and 99$\}$\\
\solution
\newline
(a) : $\{$4, 2$\}$
\newline
(b) : $\{$2, 3$\}$
\newline
(c) : $\{$4, 2, 5, 4$\}$
\newline
(d) : $\{$4, 2$\}$
\newline
(e) : $\{$4, 2$\}$
\newline\newline
Therefore set a, d and e are equal.
\newline


\newpage
\problem{2: Cardinality of Sets}{2+2+2+2=8}
What is the cardinality of each of these sets? Explain your answers.\\
\subproblem{a} $\{\emptyset\}$\\
\subproblem{b} $\{\emptyset,\{\emptyset\}\}$\\
\subproblem{c} $\{\emptyset,\{\emptyset,\{\emptyset\}\}\}$\\
\subproblem{d} $\{\emptyset,\{\emptyset,\{\emptyset,\{\emptyset\}\}\}\}$\\
\solution
\newline
(a): Since $\emptyset$ , which is an empty set, is equal to $\{\}$  so the set of a is \verb|->| $\{\{\}\}$.\newline
Elements of set a are \verb|->| $\emptyset$. Therefore cardinality of a is 1.\\\\ 
(b): Elements of set b are \verb|->| $\emptyset$ and $\{\emptyset\}$.\\
Therefore cardinality of b 2.\\\\
(c): Elements of set c are \verb|->| $\emptyset$ and $\{\emptyset,\{\emptyset\}\}$\\
Therefore cardinality of c is 2.\\\\
(d): Elements of set c are \verb|->| $\emptyset$ and $\{\emptyset,\{\emptyset,\{\emptyset\}\}\}$\\
Therefore cardinality of d is 2.\\\\


\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline




\problem{3: Cartesian Product of Sets}{15}
Explain why (A $\times$ B) $\times$ (C $\times$ D) and A $\times$ (B $\times$ C) $\times$ D are not the same.\\
\solution
\newline
\textit{We know that x operation on sets will produce an ordered pair,} \\
\textit{
Let a subset of A = \{a\}\\
Let a subset of B = \{b\}\\
Let a subset of C = \{c\}\\
Let a subset of D = \{d\}
}\\\\
The first element of two processes will be found this way below:\\
$(A \times B) \times (C \times D) = ((a,b),(c,d))$\\
$A \times ( B \times C) \times D = (a,(b,c),(d))$\\
\newline
Since ((a,b),(c,d)) $\neq$ (a,(b,c),(d)), \\
The sets are not equal.
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline

\newpage
\problem{4: Cartesian Product of Sets in Algorithms }{25}
Let A, B and C be sets which have different cardinalities. Let (p, q, r) be each triple of A $\times$ B $\times$ C where p $\in$ A, q $\in$ B and r $\in$ C. Design an algorithm which finds all the triples that are satisfying the criteria: p $\leq$ q and q $\geq$ r. Write the pseudo code of the algorithm in your solution.\newline
\newline
For example: Let the set A, B and C be as A = $\{$ 3, 5, 7 $\}$, B = $\{$ 3, 6 $\}$ and C = $\{$ 4, 6, 9 $\}$. Then the output should be : $\{$ (3, 6, 4), (3, 6, 6), (5, 6, 4), (5, 6, 6) $\}$. \newline
\newline
(Note: Assume that you have sets of A, B, C as an input argument.)\newline
\solution

\begin{algorithm}
\SetAlgoLined
\KwIn{The sets of A, B, C}
i \gets 0\\
\While{i\leq lentgh(A)}{
    j \gets 0\\
    \While{j\leq length(B)}{
        k \gets 0\\
        \While{k \leq length(C)}{
         \If{A[i]\leq B[i] \And C[i]\leq B[i]}{
            
            }
        k \gets k + 1\\
        }
    j \gets j+1\\
    }
i \gets i + 1
}

 

\caption{Pseudo Code of Your Algorithm}
\end{algorithm}

\newpage
\problem{5: Functions}{16}
If f and f $\circ$ g are one-to-one, does it follow that g is one-to-one? Justify your answer.\\
\solution
\newline
\textit{Suppose that g is not one-to-one;}\\\\
So there must be two inputs of $x_1$ and $x_2$ where g($x_1$) = g($x_2$)\\
We know that f o g is one-to-one, so there can't be two different input with the same value.\\
So inequation will be \verb|->| f(g($x_1$)) $\neq$ f(g($x_2$))  (Because fog function has two different inputs.)\\
let g($x_1$) and g($x_2$) = k since they have the same value.\\
Inequation will be \verb|->| f(k) $\neq$ f(k);\\
But we know that this inequation is wrong because f(k) = f(k)\\
Therefore g must be one-to-one.

\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline
\newline

\problem{6: Functions}{7+7+7=21}
Determine whether the function $f:$ $\mathbb{Z}\times\mathbb{Z}\to\mathbb{Z}$ is onto if\\
\subproblem{a} $f(m,n)=2m-n$\\
\subproblem{b} $f(m,n)=m^2-n^2$\\
\subproblem{c} $f(m,n)=\mid m\mid - \mid n\mid$\\
\solution
\newline
(a): For any integer value of m, where n = 0; There exist an integer value where f(m,0) = 2m\\
 For any integer value of m, where m = 0; There exist an integer value where f(0,n) = -n\\\\
(b): Since any integer  value of m and n, function f cannot be less than 0,\\ 
therefore this is not an onto function.\\\\
(c): For any integer value of m and n, function f cannot be less than 0,\\
therefore this is not an onto function.\\

\newline

\newpage
\problem{7: Functions}{Bonus 20}
Suppose that $f$ is a function from $A$ to $B$, where $A$ and $B$ are finite sets with $\mid A\mid=\mid B\mid$. Show that $f$ is one-to-one if and only if it is onto.\\
\solution
\newline
\textit{Suppose that f is not one-to-one;}\\\\\\
In that case, there must be two inputs of $x_1$ and $x_1$ where they satisfy the equation $f$($x_1$) = $f$($x_2$).\\\\
Therefore the cardinality of codomain of $f$ will be greater than cardinality of image of f.\\\\
Since there will be a value that is not matched in codomain of $f$, function $f$ cannot be onto in that case.\\\\
Hence function f must be a one-to-one function.\\

\newline

\end{document} 


